PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-12 paper/ms.tex
update paper
merge Jon Jenkins comments

%
% key authors:
%
\author[0000-0002-0514-5538]{L.\,G.\,Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%CONFIRMED
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
%
%PENDING yy
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
%
%CONFIRMED
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%CONFIRMED
\author[0000-0002-6892-6948]{S.~Seager} % seager@mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
\affiliation{Department of Earth, Atmospheric and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\affiliation{Department of Aeronautics and Astronautics, MIT, 77
Massachusetts Avenue, Cambridge, MA 02139, USA}
%
%PENDING yy
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

@@

%PENDING y
\author[0000-0003-4724-745X]{M. E. Rose} %  mark.rose@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

@@

\begin{abstract}
  PTFO$\,$8-8695 (CVSO\,30) is a star in the 7--10 million year old
  Orion-OB1a cluster that shows brightness dips that resemble
  planetary transits.  While strong evidence against the planet
  hypothesis has already been provided, the possibility remains
  debated in the literature.  To obtain further clues, we inspected
  data from the NASA {\it Transiting Exoplanet Survey Satellite}
  (TESS) and the ESA Gaia mission.  The Gaia data show that
  PTFO$\,$8-8695 is a photometric binary with respect to members of
  its kinematic group, and independently suggest that it is an
  astrometric binary.  The TESS lightcurve shows two different
  photometric periods. The variability is dominated by a sinusoidal
  signal with a period of 11.98$\,$hr, presumably caused by stellar
  rotation.  Also present is a 10.76$\,$hr signal consisting of a
  not-quite sinusoid interrupted by hour-long dips, the type of signal
  previously intepreted as planetary transits.  The phase of the dips
  is nearly 180$^\circ$ away from the phase of the originally reported
  dips. As noted previously, this makes them difficult to explain as
  planetary transits.  Instead, we believe that PTFO$\,$8-8695 is a
  pair of young and rapidly rotating M dwarfs, one of which shows the
  same ``transient-dipper'' behavior that been seen in at least 5
  other cases.  The origin of these transient dips is still unknown
  but likely involves circumstellar material.
\end{abstract}

@@

We begin in Section~\ref{sec:observations} by describing newly
available observations from TESS \citep{ricker_transiting_2015} and
Gaia \citep{gaia_collaboration_gaia_2018}.  The TESS lightcurve shows
two different periodic signals, which we analyze in
Section~\ref{sec:tess}.  The Gaia data, analyzed in
Section~\ref{sec:gaia}, show that \ptfo\ is a photometric binary, and
suggest it is also an astrometric binary.  We discuss the pieces of
the puzzle in Section~\ref{sec:discussion}, and summarize the
situation in Section~\ref{sec:conclusions}.  We comment on the study
by \citet{koen_2020} in postscript.

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS lightcurve of \ptfo\ (Sector 6, Orbit 19).} {\it Top}:
    The ``raw'' (\texttt{PDCSAP} mean-subtracted) relative flux.
    The beat period of 4.48 days is visible by eye.  The blue curve is
    a model including 2 harmonics at the longer period $P_{\rm \ell}$,
    plus 2 harmonics and a transit at the shorter period $P_{\rm s}$.
    {\it Upper middle}: Longer-period signal, equal to the raw signal
    minus the shorter-period signal.  {\it Lower middle}:
    Shorter-period signal, equal to the raw signal minus the
    longer-period signal.  {\it Bottom}: residual relative flux.  The
    data are binned from 2 to 10 minute cadence as a convenience for
    plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

\begin{figure*}[hbtp]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf TESS lightcurve of \ptfo\ (Sector 6, Orbit 20).} Same
  format as Figure~\ref{fig:splitsignal}.
  \label{fig:splitsignalii}
	}
\end{figure*}

@@

\ptfo\ [also known as CVSO\,30; \citealt{briceno_cida_2005}] was
observed by TESS with Camera 1, CCD 1, from December 15, 2018 until
January 6, 2019, during the sixth sector of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,264461976 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  The pixel data for an
$11\times11$ array surrounding \ptfo\ were averaged into 2-minute
stacks by the onboard computer.  Each 2048$\times$2048 image from the
CCD was also averaged into 30-minute stacks, and saved as a ``full
frame image'' (FFI).

The 2-minute stacks for \ptfo\ were reduced to lightcurves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) lightcurve.  The PDC lightcurve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{smith_finding_2016}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_2012,stumpe_multiscale_2014}.
% \citep{smith_kepler_PDC_2017}
% \citep{smith_kepler_apertures_2017}

As an independent check on the 2-minute SPOC lightcurve, we examined
the lightcurve based upon 30-minute image stacks which was produced as
part of the Cluster Difference Imaging Photometric Survey (CDIPS;
\citealt{bouma_cluster_2019}).  Our CDIPS lightcurve of choice used a
circular aperture with radius 1 pixel.

To clean the data, we removed all points with non-zero quality flags,
which indicate known problems \citep[{\it
e.g.},][]{tess_data_product_description_2018}.  We also masked out the
data from the first and last 6 hours of each orbit, since there are
often systematic red noise in the photometry during those times.  Both
the CDIPS and PDC lightcurves showed a clear discontinuous jump in the
last few days of orbit 20, which seemed likely to be an instrumental
systematic effect.  We correspondingly masked out the data with
timestamps ranging from BJD\,2458488.3 until the end of the orbit.
The PDC lightcurve initially had 15{,}678 points.  The quality-flag
cut removed 854 points; masking the orbit edges removed an additional
716 points; and removing the data from the final few days of orbit 20
removed an additional 1079 points.  After cleaning, 83\% of the
initial flux measurements remained.

We normalized the lightcurve by dividing out the median flux, and then
opted to subtract 1{.}0 to set the median value to zero, which
simplified subsequent interpretation.  Many of these and subsequent
processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.93\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: Relative flux at the longer period, as in
    Figure~\ref{fig:splitsignal}.  {\it Bottom}: Relative flux at the
    shorter period. The reference phase is set to the dip.  Gray
    points are the 10 minute cadence \texttt{PDCSAP} flux.  Black
    points are binned to 100 points per period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

Our initial inspection of the TESS lightcurve, in both its 2-minute
PDCSAP and 30-minute FFI forms, showed a strong sinusoidal beat signal
(Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}, top
panel). As a precursor to more detailed analysis, we calculated
generalized Lomb-Scargle periodograms using \texttt{astrobase}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015,bhatti_astrobase_2018}.
The two tallest peaks occur at 0.448\,days and 0.499\,days.  We will
refer to these two periods as the ``shorter period'' $P_{\rm s}$ and
the ``longer period'' $P_{\rm \ell}$.  The peak at $P_{\rm \ell}$ is
the taller of the two peaks.  Lower-power harmonics of both signals
are also present.

@@

The peak-to-peak lightcurve amplitude at maximum, when the two signals
interfere constructively, is about 14\%.  During the times of
destructive interference, the peak-to-peak amplitude is about 6\%.
Assuming the signals are mainly sinusoidal, simple algebra tells us
that the peak-to-peak amplitudes should be about 10\% for the
longer-period signal, and 4\% for the shorter-period signal.  To view
the phase-folded light curves of the longer-period signal, we
subtracted the best-fitting sinusoid at the shorter period; the
resulting light curve appears smooth and nearly sinusoidal.  But after
subtracting the best-fitting sinusoid at the longer period, visual
inspection of the phase-folded light curve of the shorter-period
signal revealed substructure resembling the ``dips'' seen in previous
observations. In particular, there was a $\approx$1\% dip lasting
about an hour.  These initial impressions turned out to be consistent
with the results of our more complicated analysis, described below.

\subsection{Lightcurve Model}

We fitted a model to the lightcurve consisting of a linear combination
of Fourier modes with periods $P_{\rm s}$ and $P_{\rm \ell}$, as well
as a number of harmonics chosen as described below. To try accounting
for the dips, we also added an analytic transit model with period
$P_{\rm s}$.  Symbolically, the total flux $f$ is given as
\begin{equation}
  f = f_{\rm s} + f_{\rm \ell}
  = f_{\rm transit,s} + f_{\rm Fourier,s} + f_{\rm Fourier,\ell},
\end{equation}
where $f_{\rm s}$ is the flux at the shorter period, and $f_{\rm
\ell}$ is the flux at the longer period.  Writing out the Fourier
terms explicitly,
\begin{align}
  f = &f_{\rm transit,s} + \sum_{n=1}^{N_{\rm s}} A_n \sin(n\omega_{\rm s}t)
  + \sum_{n=1}^{N_{\rm s}} B_n \cos(n\omega_{\rm s}t)\\
  &+ \sum_{m=1}^{N_{\rm \ell}} A_m \sin(m[\omega_{\rm \ell}t+\phi_{\rm \ell}])
  + \sum_{m=1}^{N_{\rm \ell}} B_m \cos(m[\omega_{\rm \ell}t+\phi_{\rm \ell}]), \nonumber
\end{align}
where $N_{\rm s}$ and $N_{\rm \ell}$ are the total number of modes at
the shorter and longer periods, respectively, $A_i$ and $B_i$ are the
amplitudes of each mode (which can be positive or negative), and
$\omega_\ell$ and $\omega_{\rm s}$ are the angular frequencies of the
longer-period and shorter-period signals. By not including a phase
parameter in the shorter-period model, we have implicitly defined the
zero point of the phase scale. The relative phase of the longer-period
model is specified by the phase parameter $\phi_\ell$.  Since we did
not know in advance how many harmonics would be appropriate to include
in the model, we considered a number of different choices for $N_{\rm
s}$ and $N_{\rm \ell}$, and used the Bayesian information criterion to
select the final model (Table~1).

@@

We implemented and fitted the models using \texttt{PyMC3}, which is
built on \texttt{theano}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the Fourier terms,
we used the default math operators.  For the exoplanet transit, we
used the model and derivatives implemented in the \texttt{exoplanet}
code \citep{exoplanet:exoplanet}.  Our priors are listed in Table~2.
To speed up the fitting process, we averaged the 2-minute lightcurve
to 10-minute samples.  We correspondingly scaled the uncertainties in
the flux measurements by a factor of $\sqrt{5}$.  Before sampling, we
initialized each model with the parameters of the maximum a posteriori
(MAP) model.  We then assumed a Gaussian likelihood, and sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, and used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.  We tested our ability to
successfully recover injected parameters using synthetic data before
fitting the \ptfo\ lightcurves.

@@

To explore where each model succeeded and failed, we split the raw
signal into its respective components (Figures~\ref{fig:splitsignal}
and~\ref{fig:splitsignalii}).  We also examined the phase-folded
signals (Figure~\ref{fig:phasefold}).

@@

The TESS pixels are $\approx21$'' per side. Before making any
interpretations, we needed to consider whether light from neighboring
stars could have contributed to the photometric signal we are
attributing to \ptfo. The scene is shown in Figure~\ref{fig:scene}.
In the upper panels, the pixels used to measure the background level
in the SPOC lightcurve are indicated with `\texttt{X}' hatching, and
the pixels used in the final lightcurve aperture are shown with
`\texttt{/}' hatching.

@@

First, we examined the CDIPS FFI lightcurves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three lightcurves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels. The maximal peak-to-peak beat amplitude was the same to
within a percent, regardless of the size of the photometric aperture
that was used to create the lightcurve.  If Star A were the source of
the long-period variability, we would expect the peak variability
amplitude to be smallest in the 1 pixel aperture, based on the
separation of the sources (Figure~\ref{fig:scene}, bottom).  From this
test alone, it seems unlikely that Star A is the source of the
long-period signal.

Second, we examined the 2-minute lightcurve of each individual pixel
in the scene, using the interactive tools implemented in
\texttt{lightkurve} \citep{lightkurve_2018}.  If Star A were the
source of the long-period variability, we would expect the pixels
nearest to Star A to show a sinusoidal signal with amplitude exceeding
$10\%$.  The data do not show this pattern.  The pixel directly below
Star A does not clearly show any sinusoidal variability; the
peak-to-peak variability in that pixel is $\lesssim 8\%$.  In
contrast, the south-easternmost pixel within the \ptfo\ aperture (the
pixel furthest from Star A that was used in the optimal aperture)
shows the longer-period sinusoidal variability signal with an
amplitude of 14\%.  We conclude that within the resolution of the Gaia
DR2 source catalog, the $P_{\rm s}$ and $P_{\rm \ell}$ signals
originate from \ptfo.  Based on the work of
\citet{ziegler_measuring_2018}, we can surmise that stellar companions
with separations wider than $\approx$1'' (349~AU) and within $\Delta G
\approx 3$ magnitudes of \ptfo\ would have likely been detected
through this approach.

@@

% NB: CDIPS-I only made 131 light-curves for 25Ori-1, because I wasn't
% aware of the Kounkel+18 member list at the time.
Using the same 149 members in the 25$\,$Ori-1 subgroup, we calculated
the astrometric reduced $\chi^2$ for each member.  We then queried the
CDIPS lightcurve database at MAST \citep{bouma_cluster_2019} to find
the subset of members that were at least as variable as \ptfo.  We
measured the variability amplitude by taking the difference between
the $95^{\rm th}$ and $5^{\rm th}$ percentiles of the flux
measurements.  This yielded 30 stars of equal or greater variability.
The lower panel of Figure~\ref{fig:gaia} shows the reduced $\chi^2$ as
a function of stellar brightness.  \ptfo\ is in the upper 90$^{\rm
th}$ percentile of stars showing astrometric excesses within the
25$\,$Ori-1 group.  Relative to other M-dwarf group members with
comparable brightnesses and variability characteristics, \ptfo\ still
stands out by virtue of its failure to conform to a single-star
astrometric model. This supports the interpretation that \ptfo\ is a
binary star.

>>>>

%
% key authors:
%
\author[0000-0002-0514-5538]{L.\,G.\,Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
\author[0000-0002-4265-047X]{J.\,N.\,Winn}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}
%
% 
%-------------------------------------
% TESS Mission Architects:
% These authors should be listed in this order
% see https://spacebook.mit.edu/pages/viewpage.action?pageId=24543276
%-------------------------------------
%
%CONFIRMED
\author{G. R. Ricker} % grr@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
%
%PENDING yy
\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
%
%CONFIRMED
\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}
%
%CONFIRMED
\author[0000-0002-6892-6948]{S.~Seager} % seager@mit.edu
\affiliation{Department of Physics and Kavli Institute for
Astrophysics and Space Research, Massachusetts Institute of
Technology, Cambridge, MA 02139, USA}
\affiliation{Department of Earth, Atmospheric and Planetary Sciences,
Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\affiliation{Department of Aeronautics and Astronautics, MIT, 77
Massachusetts Avenue, Cambridge, MA 02139, USA}
%
%CONFIRMED
\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
%
%-------------------------------------
% 3 representatives of each of SPOC, POC, TSO, for a total of 9. 
%These 9 authors should be listed in alphabetical order
%-------------------------------------
% 3 TSO COAUTHORS
%     Karen Collins karenacollins@outlook.com
%     Sam Quinn squinn@cfa.harvard.edu
%     Dana Louie danalouie@astro.umd.edu
% 3 SPOC COAUTHORS
%     Mark E. Rose mark.rose@nasa.gov
%     Jeffrey C. Smith  jeffrey.c.smith-1@nasa.gov
%     Bill Wohler  bill.wohler@nasa.gov
% 3 POC COAUTHORS: 
%     John Doty (jpd@noqsi.com)
%     Joel Villaseñor (jsvilla@space.mit.edu)
%     Tom Barclay (barclay.astro@gmail.com)

@@

%CONFIRMED
\author[0000-0003-4724-745X]{M. E. Rose} %  mark.rose@nasa.gov
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

@@

\begin{abstract}
  PTFO$\,$8-8695 (CVSO\,30) is a star in the 7--10 million year old
  Orion-OB1a cluster that shows brightness dips that resemble
  planetary transits.  While strong evidence against the planet
  hypothesis has already been provided, the possibility remains
  debated in the literature.  To obtain further clues, we inspected
  data from the NASA {\it Transiting Exoplanet Survey Satellite}
  (TESS) and the ESA Gaia mission.  The Gaia data show that
  PTFO$\,$8-8695 is a photometric binary with respect to members of
  its kinematic group, and independently suggest that it is an
  astrometric binary.  The TESS light curve shows two different
  photometric periods. The variability is dominated by a sinusoidal
  signal with a period of 11.98$\,$hr, presumably caused by stellar
  rotation.  Also present is a 10.76$\,$hr signal consisting of a
  not-quite sinusoid interrupted by hour-long dips, the type of signal
  previously intepreted as planetary transits.  The phase of the dips
  is nearly 180$^\circ$ away from the phase of the originally reported
  dips. As noted previously, this makes them difficult to explain as
  planetary transits.  Instead, we believe that PTFO$\,$8-8695 is a
  pair of young and rapidly rotating M dwarfs, one of which shows the
  same ``transient-dipper'' behavior that been seen in at least 5
  other cases.  The origin of these transient dips is still unknown
  but likely involves circumstellar material.
\end{abstract}

@@

We begin in Section~\ref{sec:observations} by describing newly
available observations from TESS \citep{ricker_transiting_2015} and
Gaia \citep{gaia_collaboration_gaia_2018}.  The TESS light curve shows
two different periodic signals, which we analyze in
Section~\ref{sec:tess}.  The Gaia data, analyzed in
Section~\ref{sec:gaia}, show that \ptfo\ is a photometric binary, and
suggest it is also an astrometric binary.  We discuss the pieces of
the puzzle in Section~\ref{sec:discussion}, and summarize the
situation in Section~\ref{sec:conclusions}.  We comment on the study
by \citet{koen_2020} in postscript.

@@

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf TESS light curve of \ptfo\ (Sector 6, Orbit 19).} {\it Top}:
    The original (\texttt{PDCSAP} mean-subtracted) relative flux.
    The beat period of 4.48 days is visible by eye.  The blue curve is
    a model including 2 harmonics at the longer period $P_{\rm \ell}$,
    plus 2 harmonics and a transit at the shorter period $P_{\rm s}$.
    {\it Upper middle}: Longer-period signal, equal to the original signal
    minus the shorter-period signal.  {\it Lower middle}:
    Shorter-period signal, equal to the original signal minus the
    longer-period signal.  {\it Bottom}: residual relative flux.  The
    data are binned from 2 to 10 minute cadence as a convenience for
    plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

\begin{figure*}[hbtp]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf TESS light curve of \ptfo\ (Sector 6, Orbit 20).} Same
  format as Figure~\ref{fig:splitsignal}.
  \label{fig:splitsignalii}
	}
\end{figure*}

@@

\ptfo\ (also known as CVSO\,30; \citealt{briceno_cida_2005}) was
observed by TESS with Camera 1, CCD 1, from December 15, 2018 until
January 6, 2019, during the sixth sector of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,264461976 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  The pixel data for an
$11\times11$ array surrounding \ptfo\ were averaged into 2-minute
stacks by the onboard computer.  Each 2048$\times$2048 image from the
CCD was also averaged into 30-minute stacks, and saved as a ``full
frame image'' (FFI).

The 2-minute stacks for \ptfo\ were reduced to light curves by the
Science Processing Operations Center (SPOC) at NASA
Ames~\citep{jenkins_tess_2016}.  We mainly used the Presearch Data
Conditioning (PDC) light curve.  The PDC light curve aperture used
pixels chosen to maximize the SNR of the total flux of the target
\citep{bryson_2020_target_aperture}.  Non-astrophysical variability
was removed by fitting out trends common to many stars
\citep{smith_kepler_2012,stumpe_multiscale_2014}.
% \citep{smith_kepler_PDC_2017}
% \citep{smith_kepler_apertures_2017}

As an independent check on the 2-minute SPOC light curve, we examined
the light curve based upon 30-minute image stacks which was produced as
part of the Cluster Difference Imaging Photometric Survey (CDIPS;
\citealt{bouma_cluster_2019}).  Our CDIPS light curve of choice used a
circular aperture with radius 1 pixel.

To clean the data, we removed all points with non-zero quality flags,
which indicate known problems \citep[{\it
e.g.},][]{tess_data_product_description_2018}.  We also masked out the
data from the first and last 6 hours of each orbit, since there are
often systematic red noise in the photometry during those times.  Both
the CDIPS and PDC light curves showed a clear discontinuous jump in the
last few days of orbit 20, which seemed likely to be an instrumental
systematic effect.  We correspondingly masked out the data with
timestamps ranging from BJD\,2458488.3 until the end of the orbit.
The PDC light curve initially had 15{,}678 points.  The quality-flag
cut removed 854 points; masking the orbit edges removed an additional
716 points; and removing the data from the final few days of orbit 20
removed an additional 1079 points.  After cleaning, 83\% of the
initial flux measurements remained.

We normalized the light curve by dividing out the median flux, and then
opted to subtract 1{.}0 to set the median value to zero, which
simplified subsequent interpretation.  Many of these and subsequent
processing steps were performed using
\texttt{astrobase}~\citep{bhatti_astrobase_2018}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.93\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded longer and shorter-period signals.}
    {\it Top}: Relative flux at the longer period, as in
    Figure~\ref{fig:splitsignal}.  {\it Bottom}: Relative flux at the
    shorter period. The reference phase is set to the dip.  Gray
    points are the 10 minute cadence \texttt{PDCSAP} flux.  Black
    points are binned to 100 points per period.
    The model (blue line)
    includes 2 harmonics at the longer period,
    plus 2 harmonics and a transit at the shorter period.
		\label{fig:phasefold}
	}
\end{figure*}

@@

Our initial inspection of the TESS light curve, in both its 2-minute
PDCSAP and 30-minute FFI forms, showed a strong sinusoidal beat signal
(Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}, top
panel). As a precursor to more detailed analysis, we calculated
generalized Lomb-Scargle periodograms using \texttt{astrobase}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015,bhatti_astrobase_2018}.
The two tallest peaks occur at 0.448\,days and 0.499\,days.  We will
refer to these two periods as the ``shorter period'' $P_{\rm s}$ and
the ``longer period'' $P_{\rm \ell}$.  The peak at $P_{\rm \ell}$ is
the taller of the two peaks.  Lower-power harmonics of both signals
are also present.

@@

The peak-to-peak light curve amplitude at maximum, when the two signals
interfere constructively, is about 14\%.  During the times of
destructive interference, the peak-to-peak amplitude is about 6\%.
Assuming the signals are mainly sinusoidal, simple algebra tells us
that the peak-to-peak amplitudes should be about 10\% for the
longer-period signal, and 4\% for the shorter-period signal.  To view
the phase-folded light curves of the longer-period signal, we
subtracted the best-fitting sinusoid at the shorter period; the
resulting light curve appears smooth and nearly sinusoidal.  But after
subtracting the best-fitting sinusoid at the longer period, visual
inspection of the phase-folded light curve of the shorter-period
signal revealed substructure resembling the ``dips'' seen in previous
observations. In particular, there was a $\approx$1\% dip lasting
about an hour.  These initial impressions turned out to be consistent
with the results of our more complicated analysis, described below.

\subsection{Light Curve Model}

We fitted a model to the light curve consisting of a linear combination
of Fourier modes with periods $P_{\rm s}$ and $P_{\rm \ell}$, as well
as a number of harmonics chosen as described below. To try accounting
for the dips, we also added an analytic transit model with period
$P_{\rm s}$.  Symbolically, the total flux $f$ is given as
\begin{equation}
  f = f_{\rm s} + f_{\rm \ell}
  = f_{\rm transit,s} + f_{\rm Fourier,s} + f_{\rm Fourier,\ell},
\end{equation}
where $f_{\rm s}$ is the flux at the shorter period, and $f_{\rm
\ell}$ is the flux at the longer period.  Writing out the Fourier
terms explicitly,
\begin{align}
  f = &f_{\rm transit,s} + \sum_{n=1}^{N_{\rm s}} A_n \sin(n\omega_{\rm s}t)
  + \sum_{n=1}^{N_{\rm s}} B_n \cos(n\omega_{\rm s}t)\\
  &+ \sum_{m=1}^{N_{\rm \ell}} A_m \sin(m[\omega_{\rm \ell}t+\phi_{\rm \ell}])
  + \sum_{m=1}^{N_{\rm \ell}} B_m \cos(m[\omega_{\rm \ell}t+\phi_{\rm \ell}]), \nonumber
\end{align}
where $N_{\rm s}$ and $N_{\rm \ell}$ are the total number of modes at
the shorter and longer periods, respectively, $A_i$ and $B_i$ are the
amplitudes of each mode (which can be positive or negative), and
$\omega_\ell$ and $\omega_{\rm s}$ are the angular frequencies of the
longer-period and shorter-period signals. By not including a phase
parameter in the shorter-period model, we have implicitly defined the
zero point of the phase scale. The relative phase of the longer-period
model is specified by the phase parameter $\phi_\ell$.  Since we did
not know in advance how many harmonics would be appropriate to include
in the model, we considered a number of different choices for $N_{\rm
s}$ and $N_{\rm \ell}$, and used the Bayesian information criterion to
select the final model (Table~1).

@@

We implemented and fitted the models using \texttt{PyMC3}, which is
built on \texttt{theano}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the Fourier terms,
we used the default math operators.  For the exoplanet transit, we
used the model and derivatives implemented in the \texttt{exoplanet}
code \citep{exoplanet:exoplanet}.  Our priors are listed in Table~2.
To speed up the fitting process, we averaged the 2-minute light curve
to 10-minute samples.  We correspondingly scaled the uncertainties in
the flux measurements by a factor of $\sqrt{5}$.  Before sampling, we
initialized each model with the parameters of the maximum a posteriori
(MAP) model.  We then assumed a Gaussian likelihood, and sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, and used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.  We tested our ability to
successfully recover injected parameters using synthetic data before
fitting the \ptfo\ light curves.

@@

To explore where each model succeeded and failed, we split the
original signal into its respective components
(Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}).  We also
examined the phase-folded signals (Figure~\ref{fig:phasefold}).

@@

The TESS pixels are $\approx21$'' per side. Before making any
interpretations, we needed to consider whether light from neighboring
stars could have contributed to the photometric signal we are
attributing to \ptfo. The scene is shown in Figure~\ref{fig:scene}.
In the upper panels, the pixels used to measure the background level
in the SPOC light curve are indicated with `\texttt{X}' hatching, and
the pixels used in the final light curve aperture are shown with
`\texttt{/}' hatching.

@@

First, we examined the CDIPS FFI light curves of the target, which are
available on MAST \citep{bouma_cluster_2019}. Three light curves are
available, based on photometric apertures with a radius of 1, 1.5, or
2.5 pixels. The maximal peak-to-peak beat amplitude was the same to
within a percent, regardless of the size of the photometric aperture
that was used to create the light curve.  If Star A were the source of
the long-period variability, we would expect the peak variability
amplitude to be smallest in the 1 pixel aperture, based on the
separation of the sources (Figure~\ref{fig:scene}, bottom).  From this
test alone, it seems unlikely that Star A is the source of the
long-period signal.

Second, we examined the 2-minute light curve of each individual pixel
in the scene, using the interactive tools implemented in
\texttt{lightkurve} \citep{lightkurve_2018}.  If Star A were the
source of the long-period variability, we would expect the pixels
nearest to Star A to show a sinusoidal signal with amplitude exceeding
$10\%$.  The data do not show this pattern.  The pixel directly below
Star A does not clearly show any sinusoidal variability; the
peak-to-peak variability in that pixel is $\lesssim 8\%$.  In
contrast, the south-easternmost pixel within the \ptfo\ aperture (the
pixel furthest from Star A that was used in the optimal aperture)
shows the longer-period sinusoidal variability signal with an
amplitude of 14\%.  We conclude that within the resolution of the Gaia
DR2 source catalog, the $P_{\rm s}$ and $P_{\rm \ell}$ signals
originate from \ptfo.  Based on the work of
\citet{ziegler_measuring_2018}, we can surmise that stellar companions
with separations wider than $\approx$1'' (349~AU) and within $\Delta G
\approx 3$ magnitudes of \ptfo\ would have likely been detected
through this approach.

@@

% NB: CDIPS-I only made 131 light curves for 25Ori-1, because I wasn't
% aware of the Kounkel+18 member list at the time.
Using the same 149 members in the 25$\,$Ori-1 subgroup, we calculated
the astrometric reduced $\chi^2$ for each member.  We then queried the
CDIPS light curve database at MAST \citep{bouma_cluster_2019} to find
the subset of members that were at least as variable as \ptfo.  We
measured the variability amplitude by taking the difference between
the $95^{\rm th}$ and $5^{\rm th}$ percentiles of the flux
measurements.  This yielded 30 stars of equal or greater variability.
The lower panel of Figure~\ref{fig:gaia} shows the reduced $\chi^2$ as
a function of stellar brightness.  \ptfo\ is in the upper 90$^{\rm
th}$ percentile of stars showing astrometric excesses within the
25$\,$Ori-1 group.  Relative to other M-dwarf group members with
comparable brightnesses and variability characteristics, \ptfo\ still
stands out by virtue of its failure to conform to a single-star
astrometric model. This supports the interpretation that \ptfo\ is a
binary star.
